% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.eng.uwaterloo.ca/~djgrant
% (c) 2003 Nathaniel Eldredge <neldredge@math.ucsd.edu> http://www.math.ucsd.edu/~neldredg/
%
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup
\setlength{\voffset}{0in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
%-----------------------------------------------------------
%\usepackage{fullpage}
%\usepackage{shading}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
%\addtolength{\resitemwidth}{-0.75in}

\usepackage{palatino}

\usepackage[usenames]{color}
\definecolor{PukeGreen}{rgb}{0.603,0.682,0.027}
\definecolor{RoyalBlue}{rgb}{0.0196,0.0157,0.6667}
\definecolor{DarkBlue}{rgb}{0,0.0118,0.3569}
\usepackage{calc}
\usepackage[colorlinks,urlcolor=DarkBlue]{hyperref}
%\usepackage{rcs}
\usepackage{url}

%\RCS $Id: cv.tex,v 1.15 2012/09/03 19:37:53 sony Exp $
%\pdfinfo{ /RCSId (\RCSId) }

\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large {\textbf{#1 \vphantom{p\^{E}}}}}}

\newenvironment{widetable}[1]
	       {\begin{tabular*}{#1}[t]{l@{\extracolsep{\fill}}r}}
	       {\end{tabular*}}

\newcommand{\ressubheading}[4]{
% magic number, sorry
  \begin{widetable}{\textwidth - 28pt}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
  \end{widetable}
  \vspace{-12pt}}

\newcommand{\ressubheadingtwo}[6]{
% magic number, sorry
  \begin{widetable}{\textwidth - 28pt}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
		\textit{#5} & \textit{#6} \\
  \end{widetable}
  \vspace{-12pt}}

\newcommand{\resitemdate}[2]{
% magic number, sorry
  \begin{widetable}{\textwidth - 28pt}
		\textbf{#1} & #2 \\
  \end{widetable}
  \vspace{-18pt}}

%-----------------------------------------------------------


\begin{document}


  \begin{widetable}{\textwidth}
    \textbf{\Large Mark Cerenzia }  & \href{mailto: cerenzia@princeton.edu}{\texttt{cerenzia@princeton.edu}} \\
    Department of Operations Research and Financial Engineering & Citizenship: United States \\
    Sherrerd Hall, Charlton Street  \\
    Princeton University \\
    Princeton, NJ 08544 USA
  \end{widetable}
\\

\vspace{0.1in}

%\noindent \rule{\textwidth}{2mm}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{\href{http://www.princeton.edu/}{Princeton University}}
		      {Princeton, NJ}
		      {Ph.D., \href{http://orfe.princeton.edu}{Operations Research and Financial Engineering}}{2013 -- 2018 (expected)}
	              \begin{itemize}
		        \resitem{Cumulative GPA: 3.918}
		        \resitem{Committee: \href{https://www.princeton.edu/~rcarmona/}{Ren\'{e} Carmona} (advisor), \href{http://www.princeton.edu/~mykhaylo/}{Mykhaylo Shkolnikov}, \href{http://www.princeton.edu/~rvan/}{Ramon van Handel}}
	              \end{itemize}
\item
	\ressubheading{\href{http://www.cornell.edu}{Cornell University}}
		      {Ithaca, NY}
		      {Ph.D., \href{http://www.math.cornell.edu}{Mathematics}}{2011 -- 2013 (started)}
	              \begin{itemize}
		        \resitem{Mathematics GPA: 4.0; Cumulative GPA: 3.953}
		        \resitem{Committee: \href{http://www.math.cornell.edu/~lsc/lau.html}{Laurent Saloff-Coste} (advisor), \href{http://www.math.cornell.edu/~cao/}{Xiaodong Cao},\href{https://www.math.cornell.edu/m/People/bynetid/lg35}{Leonard Gross}}
	              \end{itemize}

\item
	\ressubheading{\href{http://www.nd.edu}{University of Notre Dame}}
		      {South Bend, IN}
		      {B.A., \href{http://math.nd.edu/undergraduate-program/}{Honors Mathematics}, Classics (Latin), Philosophy}
		      {2007 -- 2011}
	\begin{itemize}
		\resitem{Honors Mathematics GPA: 4.0; Cumulative GPA: 3.899}
	\end{itemize}
	\item
		\ressubheading{\href{http://www.duq.edu}{Duquesne University}}
		      {Pittsburgh, PA}
		      {Honors Coursework (in lieu of senior year of high school)}
		      {2006 -- 2007}
	\begin{itemize}
		\resitem{GPA: 3.966}
	\end{itemize}

\end{itemize}
\resheading{Research Interests}
\begin{itemize}
	\item Integrable Probability, Stochastic Analysis, Control Theory, Mean Field Games
\end{itemize}


\resheading{Papers}

\begin{itemize}
	\item \textit{Hard--edge asymptotics of the Jacobi growth process} (with \href{http://www.math.columbia.edu/~kuan/}{Jeffrey Kuan}). \\Submitted to Annales de l'Institut Henri Poincar\'{e} (b). Preprint at \href{https://arxiv.org/abs/1608.06384}{arxiv:1608.06384}, August 2016.
	\item \textit{A path property of Dyson gaps, Plancherel measures for Sp($\infty$), and random surface growth}. \\ Technical report, available at \href{https://arxiv.org/abs/1506.08742}{arXiv:1506.08742}, June 2015.
  \item \textit{Differential Harnack Estimate for Endangered Species Equation} (with \href{http://www.math.cornell.edu/~cao/}{Xiaodong Cao}, \href{http://pages.uoregon.edu/demetre/}{Demetre Kazaras}). \href{http://www.ams.org/journals/proc/2015-143-10/S0002-9939-2015-12576-2/}{Published in Proceedings of the AMS, March 2015}.
  \item \textit{Discrete/Continuous Elliptic Harnack Inequality and Kernel Estimates for Functions of the Laplacian on a Graph} (with Laurent Saloff-Coste). \href{http://www.emis.de/journals/NYJM/j/2013/19-25.html}{Published in NYJM, Spring 2013}.
\end{itemize}

\resheading{Invited Talks}

\begin{itemize}
	\item \href{http://www.mathfinance2016.com/}{Sixth International IMS-FIPS Workshop}, 9 July 2016. 
	\item \href{http://www.math.cmu.edu/CCF/ccfseminar.php?SeminarSelect=1150}{Carnegie Mellon Probability and Computational Finance Seminar}, 16 November 2015.
	\item \href{https://secure.math.ucla.edu/seminars/display.php?&id=831548}{UCLA Probability Seminar}, 28 May 2015.
	\item \href{http://www.math.cornell.edu/m/node/2088}{Cornell Analysis Seminar}, 25 February 2013.
\end{itemize}

\pagebreak

\resheading{Academic Appointments}

\begin{itemize}
\item
  \ressubheading{\href{https://orfe.princeton.edu/courses}{Princeton University}}
		{Princeton, NJ}
		{Instructor}
		{2013 -- 2018}
		\begin{itemize}
			\item Math Camp for Masters in Finance Students, 2015-2017. \\
			Employer: Bendheim Center for Finance. \\
			Course reviews Mathematics required for program during two weeks preceding Fall semester.
		\end{itemize}
		{\emph{Assistant Instructor}}
              	\begin{itemize}
                    \resitem{ORF 309, F2017 (Probability and Stochastic Systems); \\ Professor Assisted: \href{http://www.princeton.edu/~mykhaylo/}{Mykhaylo Shkolnikov}}
                    \resitem{ORF 307, S2017 (Optimization); Professor Assisted: \href{http://www.princeton.edu/~rvdb/}{Robert Vanderbei}}
                    \resitem{ORF 526, F2016 (Probability Theory); Professor Assisted: \href{https://people.emich.edu/ocalin/Home.htm}{Ovidiu Calin}}
                    \resitem{ORF 405, F2015 (Regression and Applied Time Series); Professor Assisted: \href{https://www.princeton.edu/~rcarmona/}{Ren\'{e} Carmona}}
                    \resitem{ORF 505, F2014 (Statistical Analysis of Financial Data); Professor Assisted: \href{https://www.princeton.edu/~rcarmona/}{Ren\'{e} Carmona}}
               	\end{itemize}

\item
  \ressubheading{\href{http://www.math.cornell.edu}{Cornell University}}
		{Ithaca, NY}
		{Teaching Assistant}
		{2012 -- 2013}
              	\begin{itemize}
		 \resitem{Math 6710 (Graduate
                    Probability Theory I); Professor Assisted: \href{http://www.math.cornell.edu/~neldredge/}{Nathaniel Eldredge}}
                    \resitem{Math 6220 (Graduate Functional Analysis); Professor Assisted: \href{http://www.math.cornell.edu/People/Faculty/grossl.html}{Leonard Gross}}
                     \resitem{Math 4180 (Introduction to the Theory of Functions of One Complex Variable); \\Professor Assisted: \href{http://www.math.cornell.edu/People/Faculty/wahlbin.html}{Lars Wahlbin}}
		\end{itemize}
				  \item
  \ressubheading{\href{http://www.math.cornell.edu}{Cornell University}}
		{Ithaca, NY}
		{\href{http://www.math.cornell.edu/Community/enrichment.html}{Ithaca High School Outreach}}
		{Spring 2012 and Spring 2013}
		  \begin{itemize}
		    \resitem{Spring 2012 and 2013: First course in Probability Theory}
		    \resitem{Full responsibility for preparing a brief course (about six weeks) for advanced high school students at Ithaca High School. }
		  \end{itemize}
				    \item
  \ressubheading{\href{http://www.math.cornell.edu}{Cornell University}}
		{Ithaca, NY}
		{Summer Math Institute Teaching Assistant}
		{Summer 2012}
		  \begin{itemize}
		    \resitem{The \href{http://www.math.cornell.edu/~smi/}{Summer Math Institute} (SMI) aims to prepare students -- particularly those from under-represented groups in mathematics -- for graduate school.}
		    \resitem{Teaching assistant for undergraduate Real Analysis responsible for study sessions, grading, and homework help.}
		  \end{itemize}
		\item
  \ressubheading{\href{http://www.math.nd.edu}{University of Notre Dame}}
		{South Bend, IN}
		{Summer Instructor}
		{Summer 2011}
              	\begin{itemize}
		  \resitem{Instructor for
                    Honors Course in Abstract Algebra following Dummit and Foote's $\mathit{Abstract  \ Algebra}$.}
                    \resitem{Full responsibility for preparing Lectures, Assignments, etc., for six Honors Mathematics students (included rising Sophomores and Juniors).}
                  \resitem{Supervisor: \href{http://math.nd.edu/people/faculty/francis-x-connolly/}{Prof. Frank Connolly}}
		\end{itemize}
		\item
		  \ressubheading{\href{http://www.math.cornell.edu}{Cornell University}}
		{Ithaca, NY}
		{NSF REU Participant}
		{Summer 2010}
		  \begin{itemize}
		    \resitem{Member of the Geometric Analysis group tasked with pursuing research in geometric analysis (especially the Ricci Flow). }
		    \resitem{Project Advisor: \href{http://www.math.cornell.edu/~cao/}{Prof. Xiaodong Cao}.}
		  \end{itemize}

\end{itemize}
\pagebreak

\resheading{Awards and Honors}
\begin{itemize}
\item
  \resitemdate{\href{http://www.math.cornell.edu/Graduate/Funds/fellowships.html}{Cornell Graduate Recruiting Fellowship}}{\emph{2011 -- 2012}}
\begin{itemize}
\resitem {Funds awarded to first-year graduate students on the basis of scholastic ability and promise of achievement.}
\end{itemize} 
\item
  \resitemdate{\href{http://math.nd.edu/awards-and-recognition/undergraduate-awards/undergraduate-awards-2011/}{Senior General Electric Prize for Honors Mathematics Major (Notre Dame)}}{\emph{2011}}
\begin{itemize}
\resitem {A monetary gift from the General Electric Foundation, awarded to an honors major who, in the opinion of the members of the faculty, excelled in mathematics in the senior year.}
\end{itemize} 
\item \resitemdate{\href{http://nd.edu/~sumr/}{Notre Dame Seminar for Undergraduate Mathematical Research (SUMR)}}{\emph{2009 -- 2011}}
\begin{itemize} 
\resitem {Goal of preparing Mathematics students for graduate work through financial support.}
\end{itemize}
\item \resitemdate{\href{http://glynnhonors.nd.edu/beyond/final-symposium/index.shtml}{Glynn Family Honors Program Research Symposium (Notre Dame)}}{\emph{2011}}
\begin{itemize} 
\resitem {One of five Glynn Family Honors students chosen to present honors senior thesis.}
\end{itemize}

\item \resitemdate{\href{http://math.nd.edu/awards-and-recognition/undergraduate-awards/undergraduate-awards-2010/}{R. Catesby Taliaferro Prize Competition (Notre Dame)}}{\emph{2010}}
\begin{itemize} 
\resitem {An essay-oriented Mathematics competition.}
\end{itemize}

\item \resitemdate{\href{http://math.nd.edu/awards-and-recognition/undergraduate-awards/undergraduate-awards-2010/}{Notre Dame Writing Center Tutor of the Year}}{\emph{2009-2010}}

\end{itemize}

\resheading{Memberships}
\begin{itemize}
\item \href{http://www.pbk.org/}{Phi Beta Kappa (PBK)}
\end{itemize}


\resheading{Hobbies}
\\
I am an avid skier and tennis player, but piano performance/interpretation is my favorite hobby. Here are some opportunities I am grateful to have had to perform: 
\begin{itemize}


\item Notre Dame Senior Recital, 2011. Only-Chopin Concert. Some clips:
\subitem \href{https://www.facebook.com/mark.cerenzia.90/videos/vb.35108657/10100397230349342/?type=3}{Second ``nouvelles'' \'{e}tude}
\subitem \href{https://www.facebook.com/mark.cerenzia.90/videos/vb.35108657/10100397251901152/?type=3}{Winterwind \'{e}tude}
\subitem \href{https://www.facebook.com/mark.cerenzia.90/videos/vb.35108657/10100397305089562/?type=3}{Sonata 3, Movement 4}
\subitem \href{https://www.facebook.com/mark.cerenzia.90/videos/vb.35108657/10100397330358922/?type=3}{Encore: Waltz in E}

\item Cornell Mathematics Department Concerts, 2012 and 2013.

\item Princeton ORFEntertainment Night, 2016 and 2017. Some clips:
\subitem Chopin, \href{https://www.youtube.com/watch?v=gf-ZHzTomSg&list=PLwpFe8W22NfX4K9OOQKUouIrOc_pwntbs&index=3}{Cello Sonata, Movement 3} (with Evan Wood).
\subitem Schulz--Evler, \href{https://www.youtube.com/watch?v=pOAiON-sooA&index=2&list=PLwpFe8W22NfXC8-t3SJXgK-XChBY9vOAQ}{Arabesques from ``On the Beautiful Blue Danube" by Johann Strauss}
\item Princeton Mathematics Department Concert, 2016. \\ 
Piano Trio in A Minor, Maurice Ravel (with Lucia Mocz, Antoine Song). Some clips:
\subitem \href{https://www.facebook.com/mark.cerenzia.90/videos/vb.35108657/10100854009195872/?type=3}{Movement 2}
\subitem \href{https://www.facebook.com/mark.cerenzia.90/videos/vb.35108657/10100855055808452/?type=3}{Movement 4}
\end{itemize}

\end{document}
